\section{Considerations When Deploying Technology}

Obviously deploying a technology like blockchain SCM systems globally presents challenges, but it provides for great benefits as well. These benefits are not all related to costs. This is a technology that can be used to reduce environmental and human rights impacts across the supply chain \parencite{mukherjeeApplicationBlockchainTechnology2021}. As companies are coming to realize that there is real benefit to being concerned with sustainability \parencite{kolkSocialResponsibilityInternational2016}, striving to make corporate social responsibility a factor in global business decision making is moving from being a nice-to-have, but not necessary, advertising point to a central strategic business consideration. Kolk points out that issues that drive consumer and business decisions include ecosystem health, sanitation, education, energy consumption, prosperity, inclusion, justice, peace, and human dignity.

With new technologies such as blockchain SCM being specifically targeted to bring informational transparency to corporate practices, failing to take these issues into consideration for any global technology deployment demonstrates significant short-term thinking. Consumers are demanding that companies provide the information they need to make ethical purchasing decisions, and that extends to nearly all global operations \parencite{saberiBlockchainTechnologyIts2019,sahaiEnablingPrivacyTraceability2020,kimProcessModelCorporate2019}. It simply is no longer realistic to think that ethics can be segregated from business strategy for long-term success. Therefore global business decisions need to be made with a clear understanding of the ethical implications of the proposed activities: be the activity the rolling out of new technology or the building of a new manufacturing plant.

One of the real advantages of cloud computing with respect to this particular point is that many cloud providers have specific documented plans to become carbon neutral, and publish data about their carbon footprint. This allows companies that are addressing technology deployments not only the convenience of being able to release technology globally, but also the ability to do so with minimal environmental impacts. A feat that is not nearly as simple to do with corporate owned computing centers.
