\section{New Product Development}
\subsection{Design Context}
\begin{frame}
  \frametitle{Medical Products Present Unique Challenges}
  \framesubtitle{Understanding Medical Device Design Context}
  \begin{itemize}
    \item<1-> Invention is not innovation
      \note[item]<1-> {\scriptsize{Invention is typically the realm of grant funded research in University (and occassionally private company) settings. It is the dreaming up of a completely new device. Such devices have very high regulatory bars to pass for clinical trials, and must undergo significant engineering design to reach the point of being a manufacturable product. }}

    \item<2-> Innovation transforms invention to a product
      \note[item]<2-> {\scriptsize{This is the realm of the medical device manufacturer. In collaboration with research experts and medical practitioners in the field. Once a new device ahs been innovated, by combinging the ideas of one or more inventions, the design can enter the regulatory process in order to be approved as a product. Thus, when medical device manufacturers speak about R\&D as part of their operations, they are speaking about the regulatory design phase and not about pure inventive research \parencite{dasUseManufacturingTechnologiesan2010}.}}

    \item<3-> Thus, Operations Management supports unique timelines
      \note[item]<3-> {\scriptsize{In many markets products have lifecycles that are growing shorter and shorter, as innovation drives design changes on a nearly continual basis \parencite{basallo-trianaAnaloguebasedDemandForecasting2017}. And thus, operations management in such industries struggles to balance qualtiy with speed to production. However, in the medical device industry, new class III products spend an average of 246 days simply in the approval phase, not countring any of the design or development time. The primary responsibility of operations management is not to get the product to market quickly, but to ensure regulatory compliance and quality management throughout the manufacturing process \parencite{dasUseManufacturingTechnologiesan2010}.}}

  \end{itemize}
\end{frame}
