\section{Recommendations}
\begin{frame}
  \begin{enumerate}
    \item<1-> Invest in Big Data / AI technology for supply chain and quality management
      \note[item]<1-> {\scriptsize{Supply chains are inherently complex. Advances in bid data analyics and AI help address supply chain management. The case company needs to track significant data related to their supply chain, including compliance with numerous international and national regulations, as well as corporate policies that they demand from their suppliers. Big data analytics are known to not merely make such management tasks easier, but to help discover hidden opportunities for efficiencies which can simply not be found by other means \parencite{fossowambaBigDataAnalytics2018} }}

    \item<2-> Develop strategic partnerships with specialists
      \note[item]<2-> {\scriptsize{The critical engineering and operations capability of the case company is in developing functioning medical devices that advance the state of the art while at the same time serving market needs. The company can not be expected to be expert in ever aspect of every component technology, but rather needs to be expert in assembling the component technologies in innovative ways. In order to minimize costs, reduce risk, and help ensure qualtiy it behooves the company to develop strategic partnerships with those who can provide specific expertise. For example, the case company partners with Accenture to help address software development and security requirements. There is ample evidence that such collaborations produce superior results in medical device manufacturing specifically \parencite{aryaPerformanceAnalysisHigh2019}}}

    \item<3-> Invest in Big Data focused on operations management
      \note[item]<3-> {\scriptsize{While there is ample awareness of how big data can contribute to supply chain management, there is also a growing body of research that shows that significant gains can be had across all aspects of operations management utilizing big data techniques. For medical device manufacturers, there is specific opportunities to be had here due to the fact that devices must be tracked over the life of the device/patient, and not merely through entry into the retail channel \parencite{fengHowResearchProduction2018}. }}
  \end{enumerate}



\end{frame}
