\begin{frame}{Key Leadership Skills}

  \begin{itemize}
    \item The ability to foster trust, collaboration, and passion \parencite{olsenWhyNeedMore2018}
    \item The ability to communicate the value proposition of cloud transformation \parencite{khayerCloudComputingAdoption2020}
    \item The ability to empower agile teams \parencite{pulakosWhatLeadsOrganizational2019}
    \item The ability to deeply listen to client needs \parencite{gillVoiceCustomerCreating2019,Wagle2020a}
  \end{itemize}





  \note[item]{Driving transformative cloud architectures requires serious dedication, hard-work and overcoming immense challenges. Teams must trust each other intimately, collaborate deeply, and address their work with continuous passion. Experience has shown that teams that are not trusting, collaborative and passionate generally do not perform well over long-lasting complex engagements. Accenture leadership's top agenda item needs to be to ensure their core teams maintain these characteristics. As Rob Garf notes, these qualities can actually make up for some measurable lack of technical knowledge, as these teams are teams that will be willing to help each other learn what is necessary to be successful. }
  \note[item]{Cloud transformation projects can be lengthy and expensive. They carry inherent risks. It is not as simple as telling a client that if they undertake this lengthy, risky project that they will be better off. Success in such projects require leadership engagement continuously through the project life. Accenture leadership must move client leaders to embrace the vision, and to want to succeed at the transforamtion as a primary business goal. Thus, it is necessary for Accenture leaders to communicate with visceral passion the specific, unique advantages Cloud infrastructure will have for each specific client. This requires that they understand the value proposition themselves.}
  \note[item]{Agility and agile teams remains the best way to quickly provide value to clients in the technology space. It is imperative therefore that Accenture leadership continue to invest in Agile training for themselves and their consultants. }
  \note[item]{Today, success in convincing clients starts first and foremost with understanding clients' needs deeply and accurately. Therefore, Accenture leaders need to have a strong and unwaivering focus on listening to client needs from a strategic, business perspective. This will allow Accenture to craft proposals that exceed client expectations but are in-line with client demands. Thus demonstrating the value of partnering with Accenture as one's strategic technology delivery team.}

\end{frame}
