\begin{frame}{What do we have to do to sustain optimal levels of performance?}

  \begin{itemize}
    \item Establish Accenture as the leading provider of Cloud, AI, and Big-Data capabilities globally
    \item Continue the track record of delivering value to customers through successful, on-time, on-budget delivery.
    \item Continue to demonstrate Accenture's primary role of being a strategic partner
  \end{itemize}





  \note[item]{Accenture is taking advantage of the current ``down time'' afforded to many consultants by heavily investing in cloud, AI, and big-data analytics training and certification for key personnel. This training will help maintain Accenture's reputation and capability as a premere provider of cloud and AI services globally. }
  \note[item]{Accenture has a strong reputation on delivering on commitments. One advantage afforded by the COVID-19 situation has been the ability to ``downsize'' the global consultant force by eliminating jobs based on prior performance metrics. By strengthening the existing consutlancy team via eliminating weak performers, Accenture should be able to improve on its ability to deliver project work in a timely and budget conscious manner.}
  \note[item]{Accenture's primary value to clients is not as a technology provider but as a strategic partner, who helps find problems as well as providing the technological know-how to solve them. Being able to find problems for clients, demonstrates a creative advantage that partnering with Accenture brings for its clients \parencite{abdullaProblemFindingCreativity2020}. }

\end{frame}
