\begin{frame}{What Must We Do Next?}

  \begin{itemize}
    \item Continue to emphasize cloud certification training for all consultants
    \item Actively seek to grow cloud engineering capabilities
    \item Actively Identify additional acquisitions to supplement key capabilities
  \end{itemize}





  \note[item]{Cloud is ``the next big thing.'' Only about 26\% of firms that are expected to move to the cloud have done any work in that direction yet \parencite{vuPredictorsCloudComputing2020} the opportunity for Accenture in this area is immense. It is imperative that to be properly positioned, Accenture take this moment in time, when many quality consultants are on the bench due to the economic slowdown and train them in cloud technologies. This move will garner extensive returns both near, and long-term. }
  \note[item]{Getting people certified in cloud technology is not the same as establishing experience in actual engineering practices. Therefore, Accenture needs to creatively engage clients so as to get as many engineers as possible experienced in cloud transformation projects. For example, engineers who are not staffed on projects could join existing teams to provide supplementary labor at no charge to the client, allowing Accenture to grow their engineering capabilities and providing a benefit to client relations as well.}
  \note[item]{Finally, Accenture's M\&A strategy has been successful in growing Accenture's capabilities, and this should not change. Accenture needs to continue to identify companies whose acquisitions can fill gaps in existing technology knowledge, or provide unique service offerings to clients. At this point in history, many of these companies are avaiable at ``firesale'' prices, and Accenture leadership should be actively seeking out companies that would fit within the Accenture space}
  \note[item]{For the next week, the key steps leadership should take are (a) ensure training capacity for cloud certifications for existing consultants; (b) determine how to get engineers as much cloud experience as possible; and (c) instruct the M\&A teams to aggressively identify at least 5 companies that would fill existing needs to help propel growth through acquisition. }

\end{frame}
