\section{Monitoring, Reviewing, and Updating}

This plan needs to be monitored in several ways.

First, there needs to be training and talent pipeline metrics developed to demonstrate the commitment to cloud capability enhancement. Targets need to be esablished for the talent pipeline, and results of meeting those targets should be reviewed quarterly in order to demonstrate that the goals are being met. If the goals are not being met, then the plan should be revisited to determine if additional resources are necessary to meet the plan, or if the lack of traction is due to some other factors that can be addressed.

Second, there needs to be specific sales targets aimed at new clients with under \$100M present valuation. Some number of these small and mid-sized firms will be the billion-dollar powerhouses of the future. Accenture needs to be at the front of the line with respect to winning these clients. If the decision is made to engage in venture capital funding, then specific targets for firm performance must be created on a per-investment basis, and trackd accordingly.

Market percentage growth in the various geographic areas is reported on quarterly, and those growth targets do not need to change. However, regional investigation into top competitor performance, particularly Tata and Cognizant in Growth Market areas of Asia and Africa should be reported to senior leadership so that adjustments can be made to both sales and M\&A targets in the region as appropriate.

On a per-company basis, and company that exists as a competitor/partner, such as IBM, should have specific metrics developed to determine how much value Accenture is derriving directly from the partnership compared to how much market share is lost to them as a competitor. This information needs to be carefully tracked in order to ensure that Accenture is deriving sufficient value from the relationship.
