\section{Planning and Implementation}

Planning to address the needed changes to Accenture's strategy revolves around several critical steps:

 \begin{enumerate}
   \item Address the sales pipeline to identify emerging companies who will make exceptional future diamond clients.
   \item Accelerate Accenture's cloud capabiltiies to ensure market dominance.
   \item Focus on Growth Market expansion while not conceeding America and European market share.
   \item Accelerate strategic partnerships with competitors who have unique technology capabilities (eg. IBM).
 \end{enumerate}

The first of these items is straightforward to state, but will require real work to operationalize across the company as it will require cultural and mind-set shifts at all levels of the organization \parencite{adamidesLinkingOperationsStrategy2015a}. Options for this include redirecting existing sales teams to creating an ``angel fund'' venture capital team that specializes in finding and growing potential client firms.

The second item is simple to state, but will require true dedication in terms of resource spending on training and talent recruitment, as well as R\&D. Currently Accenture leads the world in the ability to deliver and support cloud services. However, there are numerous competitors that are close on the trail. Accenture needs to dedicate significant financial resources and express clear leadership direction over the importance of growing these capabilities.

The third item is not new to Accenture, but is certain to require careful and thoughtful expansion moves in growth market regions. Companies like Tata and Cognizant are strong competitors who have more direct ties to the growth market regions than does Accenture. Accenture will need to carefully consider both M\&A options in these regions as well as local operating models that will allow Accenture to compete more strongly with such competitors.

Finally, Accenture has a long history of having partnerships with companies that are both suppliers and competitors. Companies that have unique technology capabilities (such as IBM's Watson technology) often do not have the capacity to meet demand. By investing in the recruiting and training necessary to be able to fulfill that demand, Accenture can leverage these competitor/partner relationships to fuel growth.
