\renewcommand{\mykey}{bagKeyResourcesIndustry2021}
\fakesection{\citeauthor{\mykey} \citeyear{\mykey} }
\fullcitebib{\mykey}

%% \end{adjustwidth}
%% Text here
The authors explore 11 hypotheses about relationships between 35 business resources in order to explore the which favors impact manufacturers moving to Industry 4.0 (I4.0), the relationship of I4.0 to Circular Economies (CE). The researcher's hypotheses all test if positive relationships between key business resource groupings influence I4.0 adoption, then they test if I4.0 adoption impacts sustainable production. Finally they examine if sustainable production impacts CE adoption. All 11 hypotheses are found to hold. These hypotheses support two primary research questions: what resources are needed for I4.0 to support CE; and, is there a relationship between I4.0 adoption and CE capabilities. The study performed is sound, with numerous checks for bias, a strong literature review, and accepted research methods. The study lacks from being limited to South American manufacturers and limited to primarily those related to component, electronic parts, and casting manufacturers. The authors note the limited depth of research available as I4.0 and CE are both emerging concepts, and CE in particular is weakly researched. The study provides an interesting look at how successful business adoption of new trends requires a full compliment of business resources and systems to work in conjunction with each other. However, both the newness of the topic and the limitations of the study mean this work should be considered more exploratory than definitive.

\newpage
%% NOTHING FOLLOWS
