\renewcommand{\mykey}{bozicBusinessIntelligenceAnalytics2019}
\fakesection{\citeauthor{\mykey} \citeyear{\mykey} }
\fullcitebib{\mykey}

%% \end{adjustwidth}
%% Text here
The authors of this study note the lack of empirical evidence linking Business Intelligence and Analyticsi (BI\&A) adoption to firm performance. After performing a deep literature review, they propose a mechanism to understand this gap. They propose a research model that argues that BI\&A use is necessary but insufficient. It must be mediated by Absorptive Capacityi (AC), the ability to create internalized shared knowledge, and Innovation Ambidexterity (IA), the ability to innovate both radically and incrementally at the same time, in order to be successful. They test their model via a survey that is constructed based on prior demonstrated research results, and tested with standard methods. They test their survey responses for numerous types of bias using a variety of statistical tests. The research results show that BI\&A use positively impacts AC, that both positively influence IA and that IA and BI\&A have a positive relationship to firm performance. This study is valuable as the link between BI\&A use and firm performance has been lacking, and organizations rarely see the promised benefits of adoption. By having a mechanism to explain success factors, this study provides a practical tactical challenge to executives to help improve their BI\&A impact on performance. The study is limited by being conducted only in Slovenia. And while the the statistical test show that the sample size of 97 is sufficiently large for the tests conducted, there could still be undetected issues with the sample that small. The study suggests multiple paths for future research to further test and expand the model.


\newpage
%% NOTHING FOLLOWS
