\renewcommand{\mykey}{rossmannFutureSocialImpact2018}
\fakesection{\citeauthor{\mykey} \citeyear{\mykey} }
\fullcitebib{\mykey}

%% \end{adjustwidth}
%% Text here
Using a delphi research methodology, the authors gather a heterogeneous collection 73 experts from both academia and practical business realms, crossing the domains of supply chain management (SCM) and computer science, ranging in experience from a few years to the most senior levels, and presiding from 19 different countries, in order to answer two research questions: How will Big Data Analytics (BD\&A) impact the future of SCM, and how will BD\&A impact the organizational role of SC managers. A significant collection of predictions results. While the resulting predictions are intriguing, it is the robust discussion of the various disagreements between domain experts that makes this article valuable. For example, how SCM experts and CS experts disagree on the impact of AI on basic SCM functions in the future sheds light onto why cross-domain studies are useful. There is wide agreement that changing consumer demands, disruptive technologies, and the increased capabilities of BD\&A will have great impacts. But the exact degree of future change in specifics is hotly debated and in the discussion section of this paper seems tied to an individuals specific domain expertise. The study's findings are likely fairly robust given the extreme heterogeneity of the participants. However, the lack of experts in transportation, geopolitics, and other arenas that impact SCM likely mean that not all impacting domain knowledge was adequately represented.

\newpage
%% NOTHING FOLLOWS
