\renewcommand{\mykey}{shengTechnology21stCentury2019}
\fakesection{\citeauthor{\mykey} \citeyear{\mykey} }
\fullcitebib{\mykey}

%% \end{adjustwidth}
%% Text here
This paper is a literature review covering the period of 2000-2015. The authors are concerned with examining the state of research in Big Data Analytics, Business Intelligence, and Decision Making across both technical and managerial communities. The review is primarily of peer reviewed articles and conference proceedings in English; however, several unpublished studies and book chapters were included. The authors provide sections reviewing the literature around data acquisition, data storage, data processing, and data analysis. They then turn to management applications and cover text analytics, web analytics, multimedia analytics, network analysis, and mobile analytics. The authors specifically call out their finding that there is an ``urgent need for closer collaboration between the academics and the industry to advance big data research and applications.'' The review is valuable because of the depth of research it represents. The authors provide more than a dozen pages of tables and charts categorizing the literature covered, as well as a comprehensive bibliography that serves as a solid starting point for any future researcher approaching these topics. The study is of course limited by the authors choices of keywords and focus on the English language. However, this is still a valuable resource for finding entry points into BDA, BI, and decision making research.

\newpage
%% NOTHING FOLLOWS
