\begin{frame}
  \frametitle{Evolution of Microservices}
  \framesubtitle{}
  \begin{itemize}
    \item<1-> UNIX Philosophy

          \note[item]<1-> {\scriptsize{As was previously noted, UNIX developed the idea of ``Do one thing and do it well'' \parencite{mcilroyBSTJ57JulyAugust1978}. This mantra however started as an attitude towards user-space shell commands, not to enterprise applications. It was something that applied more to user-tools for administering the system than for the programs that businesses would use on the systems. }}

    \item<2-> The rise of the web

          \note[item]<2-> {\scriptsize{Over the period from the late 1960s until present day, the technology to drive the internet arose, centered on a principle of providing a robust, scaling, resilient, decentralized computer-based communications structure \parencite{leinerBriefHistoryInternet2009}. This focus on key attributes of the network would soon migrate to the software that operated on that same network. }}

    \item<3-> \hrule{1.5cm}{0.15mm} as a Service

          \note[item]<3-> {\scriptsize{As the internet matured, companies started realizing they could sell subscriptions to their computing applications. Software as a Service was born. This was soon followed by Platform as a Service and Infrastructure as a Service solutions. This move was envisioned as early as the 1980s when Sun Microsystems' John Gage coined the phrase ``The network is the computer,'' but it would take a few decades before the computing power, network bandwidth, and understanding of network deliver would be sufficient to make this vision a reality. \parencite{DoesRepurposingSun,surbiryalaCloudComputingHistory2019}.}}

    \item<4-> Microservice Cloud Architecture is the future today

          \note[item]<4-> {\scriptsize{Unlike prior iterations, microservice cloud architectures are not merely putting existing monolithic programs onto the web to be utilized as services. Rather, the distributed communications nature of web applications is being leveraged to create systems that operate as a collection of small, inter-operable, shareable network based resources. Instead of communication between components happening over a memory bus, or through disk storage, they happen over APIs and web-based connections. This is a fundamental shift.}}

  \end{itemize}
\end{frame}
