\begin{frame}
  \frametitle{Vision}
  \framesubtitle{A Leadership Responsibility}
  \begin{itemize}
    \item<1-> Innovation is Change

     \note[item]<1-> {\scriptsize{Innovation inescapably relates to change. Changes to products, processes, and so forth all involve change. There is no escaping this relationship.}}

    \item<2-> Change Management is extremely difficult

          \note[item]<2-> {\scriptsize{Those who work in change management are well aware of the statistics on failed changes. Far more change efforts fail than succeed \footnote{The author is a certified change manager and certified change management trainer}.}}

    \item<3-> The key predictor of change success is leadership vision being well-communicated

          \note[item]<3-> {\scriptsize{\textcite{kotterLeadingChange2012} demonstrated long ago that leadership vision must be clear, on-point, and communicated extensively and frequently in order for change to succeed. Change management rests on a bulwark of a solid managerial vision emanating from the highest levels.}}

    \item<4-> The vision must be participatory and inclusive

          \note[item]<4-> {\scriptsize{For an organization of any size, this vision must provide space for psychological safety for the employees who are tasked with innovation \parencite{anderssonOrganizationalClimatePsychological2020}. This of course includes everyone in a modern organization. The reason is that innovation is inherently risky, so there must be acceptance of failure as learning opportunities not reasons for punishment.}}

  \end{itemize}
\end{frame}
