\subsection{Strength}

A critical strength of Accenture's is simply their scale. Presently there Accenture does business in 190 countries \parencite{AccenturePLC2019} which is simply not matched by any other company. Accenture's chief competitors on the global stage are Capgemini, Tata, Cognizant, Deloitte, PricewaterhouseCoopers, Earnst \& Young, Infosys, and KPMG. In 2019, McKinsey \& Company has fallen out of the top 10 largest firms \parencite{consulting.comTop50Consulting}. To demonstrate the difference in global reach, Capgemini is Accenture's largest competitor, yet they operate in only 50 countries world-wide. Their total revenues for 2019 were \euro{}14.1B, or \$16.6B US \parencite{capgeminiFY2019Results2020}. Accenture's revenues are more than 2.5x's larger. Tata is smaller in terms of companies in which it operates, and has only \$22B US in revenue.

This helps explain Accenture's remarkable financial position. Following 2019, Accenture held \$15B US in current assets, with total current and long-term liabilities adding up to \$14.9B US.  Accenture holds effectively \$0 long-term debt, using a set of revolving long-term loans to finance short term acquisitions then immediately, or nearly immediately, paying them off \parencite{AccenturePLC2019}. Accenture's lack of debt and relatively deep cash reserves positions them well to weather the current market volatility.

Accenture services more of the Global Fortune 500 than any other single vendor. These are no one-off staff augmentation relationships, but deep strategic partnerships wherein Accenture bring their technology and delivery talent to the table in order to help further client's strategic goals. Many of Accenture's top clients have been with the firm for multiple decades. These relationships mean give Accenture sales and account leadership access to client incite that allows Accenture to be highly reactive to client needs in order to maintain and continue these relationships.

Lastly, Accenture is highly regarded in terms of technology delivery. Various advisory and survey companies routinely find that Accenture simply can deliver solutions better than their competitors \parencite[for example see][]{forresterresearchNowTechSAP}.
