\section{SWOT Analysis}

COVID-19's global impacts in 2020 drastically impacted Accenture's operations. Revenues across nearly all of their industry groups see effects. For the 3rd quarter of 2020, Communications has decreased revenues of 2\%, Financial Services is down 3\%, Products is down 3\%, and Resources is down 6\%. Only Healh \& Public Services is showing an increase over 2019, and is up 11\%. However, due to various offsets, free cash flow is actually up to \$2.59B for the quarter from \$1.98B for the same period in 2019. Accenture has been forced to narrow it's projected annual revenue growth to 3.5-4.5\% \parencite{accentureplcAccentureForm8K2020}. This is the second narrowing on revenue growth for the year.

Still, despite what are predominately positive financial results in the face of an economic downturn, COVID-19 presents ``a significant amount of volatility, uncertainty, and economic disruption (ibid.).'' Management continues to expect ``significantly adverse'' impacts to operations, which could result from both economic and political instability and volatility driven by COVID-19 effects \parencite{accentureplcForm10Q2020}.


Perhaps most concerning from an operational perspective is that Accenture's rate of staff utilization decreased to 88\% in the third quarter, down from 91\% for the same period in 2019. Meanwhile, the staff count is up to 513,000 from 482,000 for the same period in 2019. This means that nearly 20,000 additional people are ``on the bench'' compared to the same period as last year, and the total bench count is up to over 60,000 individuals (ibid.). In a period where revenue streams are decreasing, having this many people being unproductive is dangerous to the company. Yet, at the same time, the company's only real product is the quality of people and the depth of expertise that they possess. Having a deep ``bench'' is a critical component of long-term company success, particularly for a consulting company that is focused on delivering client value through the talent and knowledge of its people \parencite{alterBuildingStrongBench2017, accentureplcForm10Q2020}.

\hfill \break

\noindent\begin{minipage}{\linewidth}
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Strength}                                                                                                                                                                                                                          & \textbf{Weakness}                                                                                                                                                                                                             \\
\begin{tabular}[c]{@{}l@{}}\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Size and Global Scale\\Financial Stability and Available Cash\\Strong Client Relationships\\Global Reputation\end{tabular}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Excess Capacity\\Minimal Secondary Products / Markets\end{tabular}\end{tabular}                                            \\
\hline
\textbf{Opportunity}                                                                                                                                                                                                                       & \textbf{Threat}                                                                                                                                                                                                               \\
\begin{tabular}[c]{@{}l@{}}\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Expansion in Growth (Geographic) Markets\\Leading "Cloud" Revolution\end{tabular}\end{tabular}                                          & \begin{tabular}[c]{@{}l@{}}\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Undercutting by Competitors\\Tightening Market for Talent\\Global Political / Trade Instability\end{tabular}\end{tabular}  \\
\hline
\end{tabular}
\end{minipage}
