\section{Alignment of Mission, Vision, and Values}

In order to determine a strategy to follow in order to uphold Accenture's mission, vision and values, it is first necessary to understand how the eight strategic variables themselves relate to the specific content of Accenture's mission, vision, and values.

\subsection{Products}

There is a certain sense in which Accenture's ``product'' is inseparable from it's people. Accenture does not, for the most part, create products for sale in the marketplace. Generally, if a group develops a marketable product, Accenture will spin that team off into an independent company, or sell the product rights to another so that Accenture can retain the appearance of an unbiased advisor for clients. This stance supports Accenture's value of ``integrity'' and the mission statement concept of partnering with clients. By taking this approach, Accenture can position itself to be a strategic partner with clients ``wherever they are'' in order to ``create lasting value'' without trying to balance providing an ROI to Accenture from the client on product sales.

Accenture's product is really the unique strategic and tactical advice provided to each client in order to help them advance their interests.

This relates closely to the basic strategies of specialization and differentiation. Accenture specializes in being a strategic partner to its customer base. Tracy suggests that companies ``have to specialize and do a few things exceptionally well,'' by not focusing on production of salable products, Accenture can specialize on its the consulting and delivery services. This is differentiable from competitors like IBM who can not be seen as objective advisors due to their significant product offerings in the market space.

\subsection{Services}

Accenture provides three basic services: strategy consulting, technology delivery, and operations support. These services are selected specifically due to the deep expertise that Accenture possess in these areas from decades of specialization. Further, they are specifically about the transformation capabilities Accenture provides to clients to help clients ``create lasting value'' in direct support of Accenture's stated mission and the client value creation portion of Accenture's values. Additionally, this relates to Accenture's ``one global network'' value, in that Accenture can seamlessly provide the necessary service to anywhere in the world from anywhere in the world.

Consulting success, technology delivery, and operational support also depend on having high quality, well trained people. It is the creation, retention and access of expertise in these areas that provides for competitive advantage in the consulting industry \parencite{sarvaryKnowledgeManagementCompetition1999}. This again supports the specialization strategy in that Accenture's service success depends on deep specialization across all major technology stacks. It is also supporting of differentiation in that Accenture can be a ``one stop shop'' for the development of new capabilities for a client: from strategic ideation through implementation and on to operational life-cycle support. While some other competitors do all of these things as well, few can do so with the global reach and cross-industry depth that Accenture can provide.

\subsection{Customers}

As previously discussed, Accenture's customers are corporations with far reaching growth ambitions and the financial ability to engage in meaningful, long-term partner relationships with Accenture. This fact is somewhat in contrast to Accenture's mission to ``meet clients wherever they are on their paths to change'' in that it limits clients to entities who have already grown their organization to a scale sufficient to need, and be able to afford, Accenture's services.

A small company with a great idea growing a cloud-based business that has the potential to be a future billion-dollar enterprise may well need significant strategic consulting services, but they will likely fall under Accenture's radar at this point in time. Still Accenture's client selection process is well understood by Accenture, and they partner with customers specifically around value creation, which supports Accenture's values.

Accenture's customer selection and sales process aligns tightly to the segmentation strategic principle. Tracy asks ``Who exactly is your perfect customer (2015, p. 53)?'' and Accenture can easily answer this question.

\subsection{Markets}

Accenture does not place boundaries upon itself with respect to any of the markets identified by Tracy (p. 42). Accenture is a global consultancy and sees no geographic boundaries around its effective operation. Indeed, it's value of ``one global network'' stresses explicitly that the geographic market Accenture will operate within is unbounded.

Similarly, Accenture does not limit horizontal markets. It's mission statement again explicitly calls out the desire to meet clients ``in every industry across the globe.'' This is also reflected in the vision statement of ``driving innovations and impact in global development.''

With respect to vertical markets, numerous technology innovations happening today are focused directly around using technology to maximize efficiency in supply chain operations. For example, there is exceptional work being done in bringing artificial intelligence, an area of deep expertise for Accenture, to bear on supply chain management in order to minimize supply chain risk and maximize efficiencies \parencite{baryannisSupplyChainRisk2019}.

Thus, with respect to Markets, Accenture's limitless approach only really applies to the strategy of differentiation. By being global, and unbounded horizontally or vertically, Accenture is one of the few consulting companies capable of helping large multinational customers with extensive supply networks who may be functioning in multiple markets themselves.

\subsection{Finances}

Simply put, Accenture's financial strength is a massive competitive advantage that is matched by only a small handful of competitors, Tata Consulting Services and IBM being the only two that can really match Accenture's financial resources.

Accenture's deep financial capabilities allows the company to invest heavily into research and development to discover new ways to apply technology in the market place. This research ranges from primary research on developing new technologies as well as innovation research into how to apply emerging technologies in new ways.

Further, Accenture is able to purchase capabilities that it lacks and sees a need for in the market. Their heavy M\&A activity, which shows no signs of slowing down, shows that Accenture is serious about their vision of ``driving innovation,'' and the amount of training dollars they invest in their people, an ability that is drive by their financial success, supports their value of ``having the best people.''

Accenture's financial performance is brought to bear in line with their mission and aligns to multiple strategic concepts. It aligns to specialization in that Accenture can deeply invest in innovation research, allowing it to be one of the most innovative companies on the planet, winning multiple awards and building a large and profitable library of patents. It aligns with differentiation in that by being able to develop or acquire whatever knowledge the market demands, Accenture is one of the few consulting companies with the financial where-with-all to leverage their financial position bring any capability to any customer anywhere on the globe.

\subsection{People}

Accenture employs over 500,000 globally. It's values include ``having the best people,'' and Accenture works heavily to ensure that this is the case. Accenture uses its financial resources to build a massive training infrastructure for their people, including multiple campuses for in-person classes, a huge portfolio of training, and investment in external training, conferences, and classes for every one of the employees. Each employee gets and annual training budget, and that budget is often supplemented by special programs, such as the recent \$3B US investment in ``cloud first'' that includes certification training in cloud technologies for as many employees as possible. Employee advancement and pay considerations include specific references to how much training an employee has taken over the prior year. Accenture's pay and career management systems strives to be purely merit based focusing on their value of having respect for the individual.

Accenture's significant investment in people aligns to the differentiation strategy in that, again, there are few companies that can compare. Also, because of Accenture's global presence in more nations than any competitor, Accenture has recruiting access to a broader talent pool, another manifestation of the ``one global network'' value.

\subsection{Technology}

While Accenture has a large number of patents that are developed in-house. These are generally not held internally but licensed out for use across industries and even by competitors. This exemplifies the commitment Accenture has to ``building a future of shared success'' and ``driving innovations and impacts in global development.'' Ultimately, Accenture has no technological advantages over competitors. Indeed, because Accenture doesn't wish to provide in-house product development to clients (see the discussion of products above), Accenture works to be innovative and strategic with a large portfolio of technology types and across all major technology platforms.

This aligns to the concentration strategy, in that Accenture concentrates not on producing in-house capabilities but on developing expertise around commodity technologies and common enterprise level products.

\subsection{Production Capability}

When asking the question of ``how much can you . . . deliver, sell, and service in a competent fashion'' (Tracy, 2015, p. 42), the answer for Accenture is more than any other global consultancy in the world. The only competitor that matches Accenture for pure scale is Tata, but they are in fewer countries than Accenture. This shows strong alignment to Accenture's global vision.

This again supports the differentiation strategy. No matter how big a project a client seeks to implement, Accenture has sufficient resources to cover them, anywhere in the world.
