\section{The Underlying Cause}

The main causes of this situation have already ben touched upon, but it is worth repeating them clearly.

First, and arguably most importantly, there is simply a shortage of people who posses the technology skills to properly engage in BDA \parencite{dawsonAdaptivelySelectingOccupations2019}. US Census data shows that the size of an enterprise directly impacts average pay rates \parencite{uscensusbureauStatisticsBusinessesEmployment}. In technical fields the pay disparity is even greater \parencite{pofeldtBigCompaniesPay2015}, which may well make it even a greater challenge to hire the people needed for this type of work.  An even greater skill gaps exists in the Cloud Computing space, and is a leading concern for corporations \parencite{sayeghCloudTalentDrought}.

Second, the issue of multiple cloud vendors is a major cause of concern \parencite{gartnerTrendsImpactingCloud2020}. Multi-cloud strategies are strategically necessary to avoid vendor lock-in, but drastically complicate the necessary architecture and deployment of IT resources. Providing secure data access across cloud vendors in non-trivial and requires advanced IT skills and careful planning to do securely and with the necessary performance attributes to facilitate BDA activities\footnote{The author has 25+ years experience in IT consulting and is a certified AWS Cloud Architect working as a consultant with Accenture. He has been involved in multiple multi-cloud projects.}. This cause has a multiplicative impact on small-to-mid-sized companies because of the first underlying cause, a lack of adequately skilled employees.

Third, the problem of uniquely complex workloads again exacerbates the situation for small-to-mid-sized companies. Even though most US companies in this category recognize the need to use new technologies in order to survive, their transition is complicated by reliance on antiquated legacy systems that are not well suited to ``lift-and-shift'' cloud deployments \parencite{smbgroupUnifiedSystemsSpringboard2021}. Rather, they are faced with needing to move re-platform to new critical systems while at the same time switching infrastructure. And, again, they are faced with this demand while dealing with a lack of adequately skilled employees.
