\section{Conclusion}

Accentures direct competitors have a collection of unique strengths that position them well to succeed in the global market space. While there is ample opportunity to ``grow the pie,'' for all players, given that cloud computing, AI, Data Analytics, Big Data services, and Internet of Things (IOT) markets are expected to grow globally by tens of billions of dollars per year for the forseeable future \parencite{GartnerForecastsWorldwide}. Still, Accenture is currently the market leader in each of these spaces for global consulting services and must aggressively seek opportunities to remain in their market leadership position. Because cloud computing and the other technologies are global solutions, competitors who can provide price differentiation through labor arbitrage beome a bigger threat. Especially now that the experience of COVID-19 has shown many large companies that remote workers can be succesful in the IT sphere.

Accenture's potential competitors have more limited capabilities to chase Accenture into this space. Due to the highly specialized knowledge required, only boutique firms which specialize in a specific technology stack present true competition. Cloud is a global computing strategy, so regional firms have limited advantages beyond cost to offer. Due to the knowledge gap their people will present, they will not be able to make a resillient marketing case for their services in this arena. In-house development, by contrast has the potential to grow as cloud providers such as Amazon, Microsoft, and Google develop more, and better training for corporate clients who want to manage their own cloud infrastructure.

Accenture's next steps in developing a corporate strategy needs to focus on at least a few key areas: maintaining their market leadership position with respect to emerging technologies; maintain their price competitiveness with other global consultancies who make extensive use of offshore labor; and, develop and expand delivery capability and capacity through both R\&D efforts and smart M\&A targets, particularly of boutique firms that present attractive alternatives to customers and clients.
