\section{Potential Competitors}

Accenture really has three potential competitors to be aware of when considering their market space. These are regional firms, boutique firms, and in-house capabilities. The comparison can be seen in table \ref{tab:compare}.

\subsection{Regional Firms}

The global IT consulting space faces stiff competition from regional firms. Regional firms offer several key advantages over global firms when the global firm is not located in the region under consideration. The regional firms should have advantages navigating local customs, laws, and practices over the global firm \parencite{chuanhengliTrajectoryConsultingFirms2005}. Regional firms may be less costly as well, as they can often function with far fewer offices, training facilities and other back-end infrastructure. While there is some evidence that a global firm is likely to have better leadership capabilities for large engagements \parencite{dragoniDevelopingLeadersStrategic2014}, for many mid- and even large-sized IT projects such leadership capabilities are not inherently necessary for success. Work that covers significant scope is not necessarily complex work.

Regional firms typically save on labor costs by having very shallow benches of staff, and instead sub-contract work to independent contractors for much of their staffing needs. Some regional firms even utilize global outsourcing companies such as TCS to provide them with a variable sized staffing pool from which to draw upon as they land engagements. The regional firm will likely maintain office and sales staff, as well as some project oversight staff as well as senior technology architects and engineers. However, the bulk of their workforce will be temporary. This significantly lowers costs for the regional firm allowing them to be highly cost competitive.

It should be noted that this discussion does not apply to Capgemini. As discussed earlier, Capgemini is a global consulting firm and operates on that model, with a deep bench of skilled, trained staff from which to draw. They happen to only be competitive to Accenture in a limited number of areas globally. The term ``regional'' here, should be thought of much more narrowly. A regional consulting firm may only operate on the West Coast of the USA, or only in Germany, for example.

\subsection{Boutique Firms}

A Boutique consulting firm is a firm that is narrowly specialized. Most boutique firms staff similarly to larger consultancies, unlike regional firms. Boutique firms tend to be smaller in size but many are still global. They are, however, narrowly focused on only a narrow band of consulting or IT services. This very tight focus allows them to develop a high degree of expertise in their niche area, and to become known for being able to deliver successfully within that area. Companies whose needs can be narrowly defined will often seek out boutique firms in the belief that their specific expertise will bring advantages. Boutique firms are usually more price competative than global consultancies becuase their smaller size limits and narrow focus limits their cost structure. They also are frequently not public companies and thus not answerable to stockholders for quarterly results.

Accenture and other global consultancies often target boutique firms for M\&A activities as a means of acquiring specific skill sets quickly. As an example, Accenture acquired the firm Solutions IQ (SIQ) for this reason. SIQ was a leading boutique consultancy that delivered agile business transformation consulting services across the USA. Agile transformation was an area where Accenture was struggling to provide experienced leadership due to a lack of in-house experienced consultants. By acquiring SIQ, Accenture was able to address that specific need. However, until the acquisition, Accenture was finding itself often losing business to SIQ in the areas where SIQ had developed expertise.

\subsection{In-house Capabilities}

Many clients at the scale of Accenture's core customer base (firms of the size and scope of the Fortune Global 1000, large financial institutions, etc.) have the resources to fund and run sophisticated IT operations at the scale necessary to support their own business. Clients of the belief that there is a competative advantage to be had from learning to run their IT systems better than their competitors may make the choice to build in-house capabilities rather than utilize external consultants. From a delivery of functionality perspective this usually is slower and more costly in the long-run than obtaining help from an experienced consulting firm. While IT projects are nortoriously difficult to scope and budget correctly, often running over-budget and IT project ROI is rarely adequate to justify the project directly \parencite{dossantosJustifyingInvestmentsNew1991}, companies hope that developing strong in-house capabilities will eventually position them in a way to compete better.

This beleif is not without precedent. United Health Group's (UHG) Optum Advisory Services is now a crown jewel in United Health Group's business offerings and has developed into a boutique consulting service in its own right. It started out as UHG trying to take control of their own internal IT operations. As they grew their IT capabilities, they realized that they could start offering specific IT consulting services to their competitors who lacked their experience specific to the complex health care industry.

% \usepackage{array}
% \usepackage{pdflscape}
% \usepackage{longtable}

\begin{small}
\begin{landscape}
\begin{longtable}{>{\hspace{0pt}}p{0.16\linewidth}|>{\hspace{0pt}}p{0.25\linewidth}>{\hspace{0pt}}p{0.275\linewidth}>{\hspace{0pt}}p{0.254\linewidth}}
\caption{Comparison of Potential Competitors}\\
\textbf{Critical Elements}                      & \textbf{Regional Firm}                                                                                                                                                                                                                                                     & \textbf{Boutique Firm}                                                                                                                                                                                                                                                                & \textbf{In-House Development}                                                                                                                                                                         \endfirsthead
\hline
\textbf{Unique Value}\par{}\textbf{Proposition} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Lower cost\\Local knowledge\end{tabular}                                                                                                                                                           & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Technical specialization\\Moderate cost\end{tabular}                                                                                                                                                          & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}New capabilities\\\begin{tabular}[c]{@{}l@{}}Operational \\differentiation over\\competitors\end{tabular}\end{tabular}        \\
\textbf{Market Position}                        & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Low when \\considered\\individually\end{tabular}\end{tabular}                                                                                                           & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Often top in their\\area of specialization\end{tabular}\\Middle-tier generally\end{tabular}                                                                                        & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}N/A\end{tabular}                                                                                                              \\
\textbf{Strength}                               & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Cost \\Local knowledge\\\begin{tabular}[c]{@{}l@{}}Client access to \\senior leadership\end{tabular}\end{tabular}                                                                                  & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Proven expertise\end{tabular}                                                                                                                                                                                 & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Total control of all\\project aspects\end{tabular}\end{tabular}                                    \\
\textbf{Weakness}                               & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Total capabilities\\Quality of staff\\Consistency of delivery\end{tabular}                                                                                                                         & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Total capabilities\\Total capacity\end{tabular}                                                                                                                                                               & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Inaccurate budgeting\\and costing\end{tabular}\\Lack of expertise\\High failure rate\end{tabular}  \\
\textbf{Opportunities}                          & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Can grow to boutique firm\\with correct leadership\end{tabular}\\\begin{tabular}[c]{@{}l@{}}Can grow to global firm \\with correct leadership\end{tabular}\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Can become global thought\\leader for niche\end{tabular}\\M\textbackslash{}A target \end{tabular}                                                                                  & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Grow projects into new\\product offerings\end{tabular}\\Industry thought leadership\end{tabular}   \\
\textbf{Threats}                                & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}Any other regional or small\\firm with lower prices\end{tabular}\\\begin{tabular}[c]{@{}l@{}}Any firm with better\\consistency in market\end{tabular}\end{tabular}      & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}\begin{tabular}[c]{@{}l@{}}M\textbackslash{}\&A pressure when \\desiring to stay independent\end{tabular}\\\begin{tabular}[c]{@{}l@{}}Niche area losing prominence \\in marketplace\end{tabular}\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l}Cost over-runs\\Lack of deep knowledge\end{tabular}
\end{longtable}
\label{tab:compare}
\end{landscape}
\end{small}
