\begin{frame}
  \frametitle{Conclusion}
  \framesubtitle{}
  \begin{itemize}
    \item Successful adoption of technology is complex, obtain strategic consulting partners to ensure success.

          \note[item]{\scriptsize{The pathway to success is complicated. It is important to have experienced consulting help along the way. Few companies can succeed in rolling out an ERP system without significant help.}}

    \item  Focus on foundational system health first

          \note[item]{\scriptsize{An ERP roll-out will of necessity touch on almost all important critical systems within the organization. If those systems are not modernized and healthy, the risk to the rollout will be significantly increased. Ensureing overall environment modernization and health is a key initial step.}}

          \item Success requires dedicated leadership

          \note[item]{\scriptsize{Leaders must know how to provide for psychological safety and how to lead Agile methodologies well. The importance of leadership behaviors and attitudes on success is hard to overstate. Leaders need to communicate constantly to ensure the vision is understood, and the importance of the changes are internalized across the organization.}}

    \item Following successful strategies

          \note[item]{\scriptsize{We have noted successful implementations and best practices from case studies. These can be emulated to increase the chances of success.}}

    \item Timeline of years, not months

          \note[item]{\scriptsize{An ERP roll-out is a multi-year effort and should be thought of in that context. While Agile methods will allow value to be extracted from the system early, full implementation and success will not happen in a single calendar year.}}

    \item Train to facilitate user adoption

          \note[item]{\scriptsize{The factors that are most important for success are psychological. The user behaviors that will facilitate and mediate success can be trained. Training users on how to discover their own pathways to success will increase the probability of success.}}

  \end{itemize}
\end{frame}
