\section{Introduction}

Analyzing the customer base of a global consultancy is not a trivial task. Just as there are many ways to look at the structure of large company, either by structure, function, geographical region, area of specialization, social networks and so forth \parencite{soderstromOrganizationalStructureInteraction2020}, so too can a very large company's client base be examined from multiple angles.



The most basic breakdown of Accenture's client base simply by client revenue spend. Accenture's top tier of clients is designated as shown in Table \ref{tab:diamond_classification}.

This provides for the most basic of customer breakdowns, simply looking at the key customers by geographic region, as Accenture's primary consideration for dividing up their operational revenue is by geographic considerations \parencite{AccenturePLC2019}. This break down can be seen in Table \ref{tab:diamond_by_market}

Finally, the diamond clients can broken down to geographic market segments as shown in Table \ref{tab:diamond_by_segment}.

Another way to slice Accenture's client accounts are by industry. Accenture looks their customers based on 3 operational groups: Communications, Media and Technology; Financial Services; Health and Public Services; Products; and Resources. This breakdown can be seen in Table \ref{tab:by_industry}. The largest industry segment is Products, followed closely by Financial Services. This makes sense as product companies, be they manufacturers of products or retailers of products are generally not primarily in the IT business. To this end, they are frequently in need of help implementing and running their essential technology stacks. Financial Services, on the other hand, frequently have fairly high-quality IT departments, but are often looking for deeper understanding of market trends with respect to financial technology. They also have a good understanding of how to utilize strategic partners to take advantage of labor arbitrage in the technology space.
