\section{Problem Statement}

Given the uncertainty expressed by business leadership as to the value of these technologies in practice, and the gap between the perceived value as expressed by CS experts compared to business leaders, a clear problem for researchers emerges. What are the characteristic factors that must be present for a business to successfully adopt BDA, Blockchain, and AI into their SCM systems in order to see a sufficient return on investment?

This question is important and timely as SCM expenses are increasing at double-digit rates yet the impact of characteristics of the organization on SCM adoption and responsiveness are unclear \parencite{storyInfluenceSupplyChain2021}. This lack of a sound research-based answer is especially difficult on small-to-mid-sized enterprises (SME) where these technologies are known to be underutilized.  \textcite{willettsBarriersSMEsAdoption2020} identify that this lack of utilization is likely driven by a host of factors, and they are able to identify several:
\begin{APAitemize}
  \item \textbf{Data Issues:} Data lacking sufficient quality, data silos, data complexity.
  \item \textbf{Knowledge Issues:} Skills and awareness insufficient to engender confidence of success.
  \item \textbf{Regulatory Issues:} Various legal issues generally around privacy and security.
  \item \textbf{Technical Issues:} Lacking sufficient infrastructure to succeed.
  \item \textbf{Organizational Issues:} Cultural and leadership impacting adoption.
  \item \textbf{Resource Issues:} Financial constraints limiting adoption.
\end{APAitemize}

It is this proposal's intention to limit the scope of inquiry to Organizational Issues. This is for several reasons. Importantly, the first three items all amount to a single issue of awareness. There are methods, tools, and techniques to clean and prepare even the most complex data environments for data analytics use \parencite{annelaurentDataLakes2020,souibguiDataQualityETL2019}. Similarly, meeting complex legal, governance, compliance, and security requirements is a problem with available solutions \parencite{hagerSecuringPrivateMedical2020,kennedya.torkuraIntegratingContinuousSecurity2017}. Skills issues can be addressed through training, consulting, communities of practice and other methods. Finally, while financial resources are a legitimate problem when talking about expensive SCM solutions, one presumption of this proposal is that some SME's who otherwise have the financial resources to embark on an SCM BD\&A strategy are non-the-less not doing so.

Thus the problem statement is to provide research that outlines organizational characteristics that mediate success when SME's adopt BD\&A, Blockchain, and AI capabilities into their SCM IT strategy. Specifically what identifiable characteristics should practitioners be able to recognize within their own organizations which will be positive predictors of likely success, and to what degree are these predictors accurate.
