\begin{frame}
  \frametitle{Summary of Analysis Performed}
  \framesubtitle{The Steps Taken}

\begin{itemize}
  \item{SWOT}
  \item{Strategic Leadership}
  \item{Customer Analysis}
  \item{Competitor Analysis}
  \item{Industry Analysis}
  \item{Working Paper}
  \item{Internal Workshop}
  \item{Final Draft}

\end{itemize}


\note[item]{\scriptsize{Strategic planning began with a Strength/Weakness/Opportunity analysis to identify keye areas that needed to be considered in developing a strategic plan}}
\note[item]{\scriptsize{This was followed by looking at the leadership compenents that need to be in-place to achieve the initial ideas generated from the SWOT analysis. Any leadership gaps where identified and key questions raised to leadership to ensure that Accenture was prepared to tactically enacct whatever strategic plan arose from the on-going analysis.}}
\note[item]{\scriptsize{Customer analysis was performed to identify who are current customers are, and who are ideal customers should be. In this analysis it was determined that there are gaps in Accenture's approach to running the client pipeline, as has already been pointed out in this presentation.}}
\note[item]{\scriptsize{Competition analysis was performed to determine who the primary competitors are and what alternative solutions exist for potential clients. How Accenture compares to these comeptitors was analyzed to ensure that any differentiating factors are well understood.}}
\note[item]{\scriptsize{A working paper was developed outlining the key findings of the above analysis, and plans were drawn up for a workshop to develop the final draft of the strategic plan. This workshop included key leadership from multiple levels to ensure that adequate insight to Accenture's true state was available to the participants.}}
\note[item]{\scriptsize{The outcome of all the preceeding analysis is coalesced into this presentation.}}
\end{frame}
