\begin{frame}
  \frametitle{Analyzing non-Customers}
  \framesubtitle{Who we serve poorly (and why it matters)}

\begin{itemize}
  \item{Accenture's average client relationship for top-tier clients is more than 10-years.}
  \item{Average S\&P Fortune 500 lifespan is 15-years.}
  \item{75\% of UK Fortune 100 companies have disappeared in last few decades.}
  \item{New multi-billion dollar enterprises, like AirBnB, appear and grow quickly.}
    \item{Accenture is inadquately capturing early partnerships with rising stars}
\end{itemize}


\note[item]{\scriptsize{The S\&P Fortune 100 have an average lifespan of 15 years \parencite{hillHowWinningOrganizations2018}. And this is even worse for UK based companies.Yet, Accenture's most valued customers have relationships that last 10 years or more.}}
\note[item]{\scriptsize{This means the sales pipeline for new, growing companies is more important than ever before. Capturing relationships with emerging transformative companies destined for billion-dollar valuation, is essential for keeping Accenture at the top of the global counsulting pyramid.}}
\note[item]{\scriptsize{The key driver of the ablity for companies to go from utterly unknown entitites to billion-dollar enterprises is the reach and power of cloud-based development, giving small entities global reach with minimal investment.}}
\note[item]{\scriptsize{Accenture has a prime opportunity to be a key strategic partner to these companies, both in providing cloud expertise, as well as providing strategy advice, delivery of non-core, but critical enterprise services, and helping with operational efficiencies.}}
\end{frame}
