\begin{frame}
  \frametitle{Analyzing Competitors}
  \framesubtitle{Primary Competition}

\begin{itemize}
  \item{Tata Consulting Services}
  \item{Cognizant}
  \item{IBM}
  \item{Other Global Operators}
\end{itemize}


\note[item]{\scriptsize{Tata Consultancy Services is part of the larger Tata group. It is the largest consulting service in India, and has recently announced that it has exceeded Accenture's annual revenues. TCS employs over 4 million people, primarily in India, and is largely focused in the off-shoring / out-sourcing space. They are making in-roads in other areas of consulting, but lag behind Accenture in terms of the number of countries in which it operates. TCS presents a strong, extant threat to Accenture's position as the dominant technology strategy consulting partner as they begin moving into this space.}}
\note[item]{\scriptsize{Cognizant is another Indian based cosnultancy. Unlike Tata, Cognizant is focused on direct competition with Accenture as a strategic technology and operations partner for large firms. Cognizant lacks Accenture's scale, and competes based on price. They have a reputation as a scandal-ridden company with frequent, serious corruption issues. They are a challenge for Accenture when dealing with price conscious clients, but their damaged reputation gives Accenture a strong counter-argument.}}
\note[item]{\scriptsize{IBM has reinvented itself as a research and consulting firm that happens to also produce technology. As a competitor, IBM has some unique capabiltiies, including the ability to offer their own cloud infrastructure and direct access to the Watson technology development team. This makes them a serious threat for clients who are focused on cloud and AI capabilities: the precise area where Accenture is seeking to grow. Luckily, as well as being a competitor, IBM also sees itself as a strategic partner to Accenture.}}
\note[item]{\scriptsize{Other global operators such as Capgemini, KPMG, and others present various challenges. However, Accenture's capabilities and global reach generally outshine these other players. They tend to have only limited advantages in very narrow spaces, either based on global region (Capgemini) or in specific market sectors (KPMG).}}
\end{frame}
