\begin{frame}
  \frametitle{Strategic Alignment}
  \framesubtitle{A Good Fit}

\begin{itemize}
  \item{Accenture's Mission is to: ``Meet clients wherever they are on their path to change -- in every industry across the globe -- and partner wtih them to create lasting value.''}
  \item{Accenture's Vision is to: ``Build a future of shared success, focusing on the environment and driving innovation and impact in global development.''}
  \item{Accenture's Values include: ``Client value creation, one global network, respect for the individual, having the best people, integrity, and stewardship.''}

\end{itemize}


\note[item]{\scriptsize{Accenture's mission, vision and values, align toghter well to form a cohesive whole. There is litle doubt they can support a successful strategy. They have done so for the past few decades, and while they are updated slightly for 2020, the overall message remains consistent and alignable to on-the-ground action.}}
\note[item]{\scriptsize{Accenture's primary services: strategy consulting, technology delivery, and operations support, provide the capabilities to achieve Accenture's state mission objectives.}}
\note[item]{\scriptsize{Accenture's primary services also are highly dependent upon having ``one global network'' and ``the best people.'' The other values compound the impact having great people working in concert globably can have. To this end, Accenture's values cohesively support the mission and vision.}}
\note[item]{\scriptsize{Accenture's vision stems directly from years of experience seeing, and treating, clients as strategic partners with whom to create shared success. Recent changes of focuing on environmental impacts address concerns raised across multiple industries about the impact of technological advancement on sustainable practices.}}
\note[item]{\scriptsize{Acccenture has the Mission, Vision, and supportint Values, to effectively structure a successful strategy.}}
\end{frame}
