\begin{frame}
  \frametitle{Recommendations}

Ultimately, the preceeding details can be distilled down into a few specific recommendations.

\begin{itemize}
  \item{For Specialization: add a focus on developing new, growing clients who are positioned to utilize the cloud well.}
  \item{For Differention: continue as before, it's working!}
  \item{For Segmentation: develop tools to focus on small, growing clients in growth markets.}
  \item{For Concentration: Continue as before, investing heavily in people to maintain market position}

\end{itemize}



\note[item]{\scriptsize{It is a testement to the well-run nature of Accenture that little needs to change in order to remain succesful. Accenture has the benefit of being in a market leadership position and can leverage the power that comes from that to help fend off challenges. Still, we must be vigilent with respect to what does need to change in order to stay relevant and in the market leadership position.}}
\note[item]{\scriptsize{Focusing on AI, Cloud and other emerging technologies and providing value propositions to established partners to invest in those technologies is a necessary and essential component of our future strategy direction. However, it is not by itself sufficient. The changing nature of the industry cycle, which is enabled by the realization of the power of cloud computing, means that Accenture needs to focus on smaller clients with growth potential. Thus the largest change from current strategy is to expand the ``cloud first'' initiative in such a way as to capture small businesses with global potential.}}
\end{frame}
