\begin{frame}
  \frametitle{Specialization Strategy}
  \framesubtitle{Where are We Focused?}

\begin{itemize}
  \item{Accenture specializes in:}
    \begin{itemize}
      \item{Technology Stategy Development}
      \item{Techology Delivery}
      \item{Operational Life-Cycle Support}
      \item{Long-term Strategic Partnerships}
    \end{itemize}
  \item{What Is Changing:}
    \begin{itemize}

      \item{Customer Selection: engage smaller clients on the risei}
      \item{Technology Stategy Development: ``Cloud First'' as the new standard}

    \end{itemize}
\end{itemize}


\note[item]{\scriptsize{From the perspective of specialization, Accenture is in a good position. Accenture is focused on end-to-end technology delviery, from strategic conception through implementation, and full life-cycle operational support. This niche is ever-growing and Accenture can do well here for a long time to come.}}
\note[item]{\scriptsize{With respect to client selection, Accenture currently specilizes in long-term client relationships. As we've seen, there is risk here as large clients don't have the stability or longevity that they used to possess. To that end, Accenture needs to engage in developing relationships with ``up-and-coming'' firms that have significant growth potential.}}
\note[item]{\scriptsize{Accenture has brought more and more focus to advanced technologies such as cloud computing and AI/Automation over the years. However, it is now time to move strongly into a stance of ``cloud  first,'' meaning that clients will be encouraged to utilize cloud computing technology first over all other options. This is due to three reasons. First, it is cheaper in the long run for the client. Second, it is more robust and failsafe for the client. Third, Accenture's heavy investment in training makes them a leader in the ability to delivery cloud capabilities.}}
\note[item]{\scriptsize{By focusing on ``cloud first'' as well as expanding our client pipeline to smaller, growing companies, Accenture's will slightly shift specialization strategy to provide a clear directional choice for clients, and a easy marketing messaage to illuminate the value of choosing Accenture over competitors who do not have the same ability to delivery on cloud solutions.}}
\end{frame}
