\begin{frame}
  \frametitle{Segmentation Strategy}
  \framesubtitle{How to divide up the pie}

\begin{itemize}
  \item{Accenture's segments the market space by:}
    \begin{itemize}
      \item{Developing long-term relationships with large, established firms}
      \item{Being seen as a necessary strategic partner with unique skillsets to support the client}
      \item{Capable of operating across all industry boundaries}
    \end{itemize}
  \item{What's Changing}
    \begin{itemize}

      \item{Accenture needs to target growing cloud-oriented companies.}
      \item{Accenture needs to target growing companies in growth-market areas (Africa and Asia)}
      \item{Accenture needs to come to terms with the new lifecycle norms of the fortune 1000}

    \end{itemize}
\end{itemize}



\note[item]{\scriptsize{Accenture's historical focus on long relationships with established companies will not be abandoned. But it must be augmented to deal with the reality of the faster business velocity of today's marketspace. Whereas in the past it took decades for companies to go from startups to global leaders, today, this can happen literally overnight. }}
\note[item]{\scriptsize{Accenture will provide special targeted sales teams at the local level to discover companies with ideas worth supporting. This will happen globally, but with special emphasis in the growth market regions where Accenture has identified the need for further expansion. }}
\note[item]{\scriptsize{These local sales teams will help Accenture develop partnerships with innovative companies with sound future prospects so as to ensure that Accenture is already seen as a valued strategic partner when and if the company reaches global scale. }}
\note[item]{\scriptsize{This focus can also include a number of the existing programs Accenture has already produced which focus on local minority and veteran owned business support.}}
\end{frame}
