\begin{frame}
  \frametitle{The Tactical and Operational Questions}
  \framesubtitle{Where Might We Focus}

\begin{itemize}
  \item{The New}
  \item{The Old}
\end{itemize}


\note[item]{\scriptsize{Accenture's program of ``Leading in the New'' features a focus on AI, automation, cloud computing, a people-first approach to all client engagements, collaborating cross-functionally, and prioritizing the digital capablities of clients. This focus makes tremendous sense due to the nearly unlmiited value proposition that cloud computing and AI bring to the table \parencite{dongBusinessValueBig2020}.}}
\note[item]{\scriptsize{As previously noted, Accenture is uniquely positioned to assist clients of developing, deploying, successfully supporting, and incorporating big-data and cloud solutions into their workstream for maximum value production. This arena provided for more than 65\% of Accenture's recent growth, and there is no appearant ceiling to this market at this time.}}
\note[item]{\scriptsize{Accenture has long demonstrated that it is a lasting value driver in long-term strategic relationships with clients. This long-standing focus on client relationships over profiting from a single engagement is a key driver in the Accenture value proposition. This old idea remains essential to effectively differentiate Accenture in the marketplace and must therefore remain a key tactical focus. This is because value creation in technology is a relational effort \parencite{ramaswamyOfferingsDigitalizedInteractive2018}.}}
\note[item]{\scriptsize{Operationally speaking, Accenture, like all companies, is learning how to do business in the age of COVID. With limited travel, remote work, and a a reworking of human services are now the new normals for managing work and workers \parencite{poleyReimaginingServiceDelivery2020}. Accenture has done well to transition and is poised to help others do the same.}}

\end{frame}
