
\section{Criteria \& Predictions}

\subsubsection{Criteria Selection}

In his book, \textcite{Tracy2015} notes that there are multiple dimensions to consider in strategic planning: analyzing the current business; analyzing the current financial statements; analyzing ROI by product and service; analyzing ROI by customer demographics; analyzing market position; analyzing future trends for the business; and exploring an idealized future identity. Of these items, three stand out as being most critical fof Accenture PLC.

\subsubsection{Future Idealized Identity}

Without question, the most important item on Tracy's list is the question of what should a global technology consultancy be in the future. This is the most critical component for one inescapable reality: the current computing revolution means that any company that is going to be competitive in this space in the next five years will need different capabilities than it currently has. The world is shifting from a world of on-premises mainframes, web-services, and desktop computing to a world of Software as a Service (SaaS), Infrastructure as a Service (IaaS), Desktop as a Service (DaaS), and Platform as a Service (PaaS), all supported by an expansive set of interconnected smart devices, the Internet of Things (IoT) \parencite{yangSoftwaredefinedCloudManufacturing2020,rajanServerlessArchitectureRevolution2018,nirenjenaCloudComputingRevolution2017 }.

Without understanding what capabilities will be needed to succeed as a strategic partner in this developing space, it will not be possible to thrive long-term as a global consultancy. The changes in this area are happening at an amazing pace. It is fully expected that in the next five years, the vast majority of our current clients will be transforming their entire IT investment strategy to take advantage of cloud and edge computing solutions.

\subsubsection{Customer Analysis}

Customer Analysis is the next most important consideration for Accenture. As cloud and edge computing become more and more prominent, the necessity of being a member of the global Fortune 1000 to support a global IT infrastructure diminishes. Where it was once necessary to have the financial ability to build data-centers on multiple continents, that is no longer the case. Cloud computing shifts capital expenditures to leasing costs for IT capacity.

This suggests that both who are customers will be and what they will need from us may well change in the coming years. It is becoming more and more possible for a small team to go from an idea to a global, billion dollar enterprise. A prominent example of this effect is Airbnb \parencite{zervasRiseSharingEconomy2017}. In 2011, Airbnb had become a billion dollar enterprise with only 250 employees. This sort of success story is very common. Accenture has to develop the skills and agility to engage small employers with big ideas to retain their position as a thought leader in technology strategy.

\subsubsection{ROI by Product and Service}

As the economics of computing change in response to the cloud revolution, Accenture needs to seriously consider what services will be able to remain profitable in the future, and which will need serious reworking, or possibly abandoning. For example, Accenture's infrastructure services are currently primarily focused on on-site, in-house infrastructure management. However, the rise of IaaS solutions, and their large-scale adoption, will mean that market must, of necessity, diminish, if not disappear.

\subsection{Predictions}

It is expected that Accenture will see itself more as a provider of customized cloud and edge services than as a consulting firm. While Strategy and Market consulting will continue to be a part of Accenture's brand, Accenture will decide to move heavily into developing their own SaaS, IaaS, DaaS, PaaS, and IoT offerings. Massive investment in cloud training, R\&D, and investments in M\&A activities that support these service offerings have already happened. This trend should not abate any time soon. Accenture will decide that their future is as a combination of a consulting company with a strong offering of customizable, readily deployable solutions for common service needs.

As for customer engagement, Accenture is likely to change both their regional customer engagement model, and their advertising model, so that they can become aware of, and market to, emerging small organizations with big ideas. This is an area of focus that will require a great deal of creativity and insight, as it is important to engage the entrepeneurs who are building the future billion-dollar service companies early. To this end, it is possible that Accenture may see the need to develop a venture capital capability to support startups, and then leverage their consulting services to help grow those startups successfully.

With respect to Product and Service mix, Accenture will continue to shift to cloud and edge based products and services. Within the next five years those offering will become the primary drivers of Accenture's revenue. This will happen both because of market demand, and because Accenture's ability to maintain it's market lead comes in no small part from their ability to continually project themselves as a thought leader.
