\section{Section 1: Workshop Approach}

\subsection{Expectations}

Key expectations for this workshop is to conclude with a full understanding and general consensus for the leadership team of: the key drivers for current business success of Accenture PLC; the key customer demographics that lead to our success; the key drivers for customer selection in the global technology consulting market; and the key capabilities Accenture PLC will need to develop over the next 5 years to ensure continued success.

\subsubsection{Consensus}

\textcite{sriviboonStrategyPerformanceInterrelation2020} showed that business strategy is a driver for firm performance, but that firm performance is not directly impacted by business strategy. Rather, the resulting performance is mediated by solidarity within the firm. One likely reason for this mediating effect of solidarity is that execution of strategy is a ``team sport,'' requiring numerous leaders to perform their roles well and in concert to achieve the desired outcome. Thus, by looking to build consensus in this workshop, Accenture leadership will be helping ensure that the necessary groundwork for long-term cooperation between leaders will be in place.

\subsubsection{Current Success}

\textcite{Tracy2015} argues that understanding the current position of the firm is necessary in order to determine future direction. Accenture PLC leadership is likely already in agreement as to the historic reasons for our current position in the market, as well as having specific rationale for our present success. However, given the recent events of COVID-19's impact on global markets and economies, revisiting this discussion to ensure the exact present market position drivers are understood is intrinsically valuable.

\subsubsection{Key Customer Demographics}

\textcite{AccenturePLC2019} has deeply documented its key customer demographics. However, again due to market shifts based on COVID-19, understanding what the future outlook for the various sub-groupings of customers is critically important for maximizing firm growth in the immediate future.

\subsubsection{Customer Selection}

Accenture's primary role is not as a supplier to a customer, but as a long-term strategic partner. ``Technology abilities of potential partners matter significantly when selecting strategic partners'' \parencite{weiConceptualFrameworkTwostage2020}. This means understanding what drives the selection of strategic partners in today's market is of paramount important for Accenture in setting a go-forward strategy.

\subsubsection{Capability Mixture}

Accenture has a solid pulse on future technology drivers. However, when setting a strategic plan, ensuring that planned investments into developing capabilities aligns with future market demands for those capabilities is critical for maximizing future profitability and growth. Thus it is essential that Accenture spend the time to map investment into emerging technology with the expected future market demand to ensure internal investments are allocated appropriately.

\subsection{Minimizing Social Power Distance}

Social power distance is a social construct that arises out of the particular culture of an organization. Accenture already has a low power distance culture with high trust levels. However, the role of power distance in facilitating open, honest communication can not be ignored. This workshop will take three specific steps to minimize social power distance among participants. The participant list for this meeting will include the key board members, all C-suite executives, executive leadership from each geographic region, executive leadership from each product sector, and the market unit lead for each market unit. This will be 31 individuals from all over the world.

\begin{enumerate}
  \item{The workshop will be facilitated by the market unit leads. These are the least senior members of the team, but are the individuals directly responsible for the execution of strategy in the market space. This will place control of the proceedings in the hands of those responsible for realizing the plan.}
  \item{The workshop will have a dress code consisting of jeans and shirts available from the Accenture employee store. Attendees will be asked to limit jewelry to wedding bands and discrete items of religious or personal significance. This will minimize any showing of wealth disparity across the team.}
  \item{While the board will retain final approval authority, the workshop will not be considered successful unless there is consensus across the participants, including the board members, on the decisions reached. When multiple approaches to a question appear, the team will break up into self-selecting sub-groups, with each sub-group including at least one board member to create and present an argument for their approach. This will ensure that those with the most power are advocating for the voices of those with less power.}
\end{enumerate}

\subsection{Ground Rules and Conflict Resolution}

The basic ground rules will be established by the facilitating team. Common Accenture tools will be used for facilitating discussion and making anonymous comments to be displayed on communication boards utilized for the meeting. Teams will self-select into roughly even sized groups, each to include at least one board member when there is dissent on an issue. These smaller teams will self-organize around how they will reach a consensus viewpoint, and be given sufficient time to do so. Teams will then present their consensus views and there will be a time-boxed open discussion on the merits of each position presented.

Once this has happened, all participants will provide rank-choice voting of all the presented positions. This will ensure a balance between the quantity and quality of support for a particular position \parencite{merlinCompromiseRulesRevisited2019}. After this decision is concluded there will be a ``thumbs up/thumbs down'' confidence vote from the audience, with any participant being given the power to make a plea to reconsider the vote. If there is support for a re-vote, this will happen. At the end of each day, the board and c-suite executives will hold their own vote on all decisions made over the day. Any decisions not receiving majority support from this group will be revisited the following morning, with clear, concise descriptions as to what precisely is at issue.

This approach will ensure that decisions are made with highest degree of support from the most people, and will create the greatest likelihood of consensus around the final plan.

\subsection{Kick-off}

The workshop will begin with a set of ice-breaker activities designed to be both mentally and physically engaging. Getting people meeting each other, discovering something about each other as unique individual people, and supporting Accenture's stated desire of ``bringing your whole self to work.''

Following these fun activities, the workshop facilitators will provide a reminder of the purpose and goals of the workshop, the ground rules and voting procedures, and answer any questions. Participants will arrive being expected to have already completely read preparatory material, including prior annual reports and market analysis reports provided by the facilitators.
