\begin{frame}
  \frametitle{What Prevents Perfection}
  \framesubtitle{Are We Still Stuck Here?}
  \begin{itemize}
    \item<1-> Root Cause Investigations are Insufficient

          \note[item]<1-> {\scriptsize{The common approach to cybersecurity incidents is to search for root cause(s) of the failure in order to remediate the presumed point of failure. As noted early, this choice of problem framing is filled with assumptions. The assumption that the failure can be remediated. The assumption that the failure is from a single or simple number of causes. The assumption that the system can be adequately decomposed to independent causal agents and more. These assumptions prevent the industry from moving beyond the notion of root cause and on to preventative action.}}

    \item<2-> Other High-Risk Industries Do It Differently

          \note[item]<2-> {\scriptsize{In the aviation industry, after an incident or accident, an investigative body looking into the causes of an aviation incident are not looking for a single cause, but a chain of causality. It is presumed that there would be multiple places where an accident or incident could have been prevented. There is rarely a single ``root cause,'' rather there is a complex tapestry of multiple, interleaving events and actions that lead to an event. While ultimate responsibility will generally fall on the last person or persons in the chain who could have prevented the event, that doesn't stop the investigators from noting how many others were in positions to change the outcome along the way. Further, the governing boards provide that  ``It is not the function of the Board to assign fault or determine civil or criminal liability, but the Board shall not refrain from fully reporting on the causes and contributing factors merely because fault or liability might be inferred from the Board's findings ... No finding of the Board shall be construed as assigning fault or determining civil or criminal liability.'' \parencite{dempseyIndependenceAviationSafety2010}. }}

  \end{itemize}
\end{frame}
