\begin{frame}
  \frametitle{Blockchain}
  \begin{itemize}
    \item<1-> Developed by an anonymous researcher in 2008 as the basis of bitcoin

    \item<2-> Provides a fault-tolerant, secure, reliable, immutable, shared database

          \note[item]<2-> {\scriptsize{Blockchain can be thought of as a public ledger where transactions are recorded. This ledger is shared with who ever wants a copy. Everyone can create transactions in the ledger. Once created, a transaction can't be altered by anyone, and the system is architected in such a way as to ensure the reliability and security of the data. }}

    \item<3-> Supply-Chain is a natural fit for blockchain

          \note[item]<3-> {\scriptsize{Numerous supply-chain issues can be addressed by using blockchain. This increases efficiency greatly, as well as allows for transparency in the network. This provides benefits to suppliers, producers, and consumers.
          }}

    \item<4-> Early adopters have seen significant advantages

         \note[item]<4-> {\scriptsize{Companies such as Maersk and Starbucks have seen huge benefits to utilizing blockchain in their supply chain \parencite{papathanasiouNonApplicationBlockchain2020,fossowambaDynamicsBlockchainAdoption2020}.}}

    \item<5-> Still, adoption is slower than expected and is slowing down. Researchers want to know why

          \note[item]<5-> {\scriptsize{Researchers have shown that the investment in blockchain technology is decreasing, and the reasons for this phenomenon has become an area of significant inquiry}}
  \end{itemize}
\end{frame}
